Our Baye's Network contained four nodes: Tampering, Time of Day, Motion Detection, and Theft.

Factors:
  Whether or not the Pi or camera has been tampered with
  The time of day
  Whether or not a person has been detected
  Whether or not something has been stolen

CPT Tables:
  Time of Day:
    P(D) = .50, P(N) = .50

  Tampering:
    P(T) = .10, P(F) = .9

  Person Detected:
    P(T|Day and tampered) = .2
    P(T|Day and not tampered) = .95
    P(T|Night and tampered) = .05
    P(T|Night and not tampered) = .15

  Something Stolen:
    P(Theft|Person detected, Day and tampered) = .75
    P(Theft|Person detected, Day and not tampered) = .05
    P(Theft|Person detected, Night and tampered) = .99
    P(Theft|Person detected, Day and tampered) = .8
    P(Theft|Person not detected, Day and tampered) = .5
    P(Theft|Person not detected, Day and not tampered) = .01
    P(Theft|Person not detected, night and tampered) = .75
    P(Theft|Person not detected, night and not tampered) = .15

Node Justification:
  Time of day:
    Thief is more likely to happen during night and can also have an effect on
    the amount of people there to work in the garden.

  Tampering:
    If the Pi or camera is tampered with it is more likely that something is
    stolen. However, it could have been tampered by natural factors (ex. the
    wind blowing it over)

  Person Detected:
    If it is night and the equipment was tampered with, it is less likely that
    there will be a person detected because there will be less people in the
    garden and it will be harder for the program to detect people. Also, it will
    be harder to detect people when the equipment has been tampered with.

  Something is Stolen:
    It is more likely for theft to happen at night especially if the equipment
    has been tampered with and it manages to detect a person. If it is day and
    the Pi detects a person it is likely that the person is there to work in the
    garden. Even if the Pi was been tampered with, although it is slightly more
    likely that something is stolen, it is still not likely that something was
    stolen.   